Introductory Physics Labs: A Tale of Two Transformations

### 2021-03-25 manuscript/onlineLabPaper.tex
Addressed reviewer comments 2 and 3 (mostly) in the MS.

Proposal development also occurred online asynchronously.  Each group produced their proposal
and posted a proposal form on a discussion board for approval. The GTA reviewed proposals and
provided feedback or approval. Groups used the GTA feedback to revise their proposals until
they were approved. Most proposals obtained approval after two or three revisions, but some
required as many as seven revisions to obtain approval. When the GTA approved a group's
proposal, they assigned the group a data set for the investigation, and the group began
measurements and analysis. Based on our prior experience running the class, we prepared some
data sets appropriate to the different proposals that previous students had produced and
provided measurements to the current students in the most raw form possible to require them to
make decisions about data collection and analysis.

@@

We developed lab kits with supplies that allowed students to perform the investigations outside
the teaching laboratory so we could provide students with a hands-on experience. We purchased
the lab kit items in collaboration with our campus bookstore, and the students purchased the
lab kits from the bookstore. We ordered lab kit items in bulk and, where possible, directly from
manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
provide online for this course.  The online adaptation of the face-to-face ADI curriculum has
changed slightly. Pre-labs are done in groups asynchronously.  Proposals are developed in
groups during the lab period, and scheduled argumentation sessions occur via WebEx during the
lab period.

>>>>

Proposal development also occurred online asynchronously.  Each group produced their proposal
and posted a proposal form on a discussion board for approval. The GTA reviewed proposals and
provided feedback or approval. Groups used the GTA feedback to revise their proposals until
they were approved. As with the prior face-to-face labs, the GTAs were looking for specific items in 
the proposals such as what data the students planned to collect, how they would use the data to 
answer the guiding question, what steps they would take to minimize errors, and how the students 
would quantify their uncertainty. Most proposals obtained approval after two or three revisions, but 
some required as many as seven revisions to obtain approval. When the GTA approved a group's
proposal, they assigned the group a data set for the investigation, and the group began
measurements and analysis. Groups were encouraged to revise their methods during the the 
measurement/analysis phase if the discovered a flaw or a better way to answer the guiding question. 
Based on our prior experience running the class, we prepared some
data sets appropriate to the different proposals that previous students had produced and
provided measurements to the current students in the most raw form possible to require them to
make decisions about data collection and analysis. We provided six data sets for the third investigation 
and 13 data sets for the fourth investigation for the Physics 1 laboratory. We provided seven data sets 
for the third investigation (each group was assigned two data sets at random to compare) and 14 data 
sets for the fourth investigation for the Physics 2 laboratory.

@@

We developed lab kits with supplies that allowed students to perform the investigations outside
the teaching laboratory so we could provide students with a hands-on experience. We purchased
the lab kit items in collaboration with our campus bookstore, and the students purchased the
lab kits from the bookstore. We ordered lab kit items in bulk and, where possible, directly from
manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
provide online for this course. Lab kit materials were used for each investigation. The two video 
analysis investigations in the Physics 1 laboratory (comparing the accelerations of a marble 
rolling up and down an incline and a marble collision in two dimensions) required the students to 
record their own videos of marbles from their lab kits using their smartphone cameras. The image 
analysis investigation in the 
Physics 2 laboratory required students to cut their own slits in aluminum foil and also create mounts 
for hairs to produce diffraction patterns with lab-kit lasers. The online adaptation of the face-to-face 
ADI curriculum has changed slightly. Pre-labs are done in groups asynchronously.  Proposals are 
developed in groups during the lab period, and scheduled argumentation sessions occur via 
WebEx during the lab period.
